Commit Rater

### 2015-08-26 presentations/paper/conclusion.tex
Add sad weka results to Conclusion

Both research questions were successfully answered: commits were recognized by the aformentioned criteria and by using machine learning, we successfully validated our personal criteria by correlating it with the criteria from reputable sources\TODO{maybe fix when it's done}.

>>>>

Only one of our research question has been answered positively: ``good'' commits were recognized by the aformentioned criteria. However, not all of our criteria could be validated by using machine learning attribution, some simply due to the criteria itself not being good, some due to the approach of machine learning not being applicable to the data set.
